\section{Background}
\label{sec:background}

\subsection{Variational Quantum Algorithms}

Variational Quantum Algorithms (VQAs) are hybrid quantum-classical algorithms that leverage parameterized quantum circuits optimized by classical optimizers~\cite{cerezo2021variational}. The general workflow consists of: (1) preparing a parameterized quantum state $\ket{\psi(\boldsymbol{\theta})}$, (2) measuring an observable to compute a cost function, and (3) updating parameters via classical optimization.

\subsubsection{Variational Quantum Eigensolver (VQE)}

VQE seeks the ground state energy $E_0$ of a Hamiltonian $H$:
\begin{equation}
E_0 = \min_{\boldsymbol{\theta}} \bra{\psi(\boldsymbol{\theta})} H \ket{\psi(\boldsymbol{\theta})}
\end{equation}
where $\ket{\psi(\boldsymbol{\theta})} = U(\boldsymbol{\theta})\ket{0}^{\otimes n}$ is the parameterized quantum state prepared by a unitary ansatz circuit $U(\boldsymbol{\theta})$.

For molecular systems, the Hamiltonian is expressed as a sum of Pauli strings:
\begin{equation}
H = \sum_i c_i P_i, \quad P_i \in \{I, X, Y, Z\}^{\otimes n}
\end{equation}

The expectation value $\langle H \rangle$ is computed by measuring each Pauli term independently and summing the weighted results.

\subsubsection{Quantum Approximate Optimization Algorithm (QAOA)}

QAOA prepares the variational state:
\begin{equation}
\ket{\boldsymbol{\gamma}, \boldsymbol{\beta}} = \prod_{p=1}^{P} e^{-i\beta_p H_M} e^{-i\gamma_p H_C} \ket{+}^{\otimes n}
\end{equation}
where $H_C$ encodes the optimization objective (cost Hamiltonian) and $H_M = \sum_i X_i$ is the mixer Hamiltonian promoting exploration.

For MaxCut on graph $G=(V,E)$:
\begin{equation}
H_C = \sum_{(i,j) \in E} \frac{1}{2}(1 - Z_i Z_j)
\end{equation}

The algorithm optimizes $(\boldsymbol{\gamma}, \boldsymbol{\beta})$ to maximize $\langle H_C \rangle$, corresponding to the expected cut value.

\subsection{Edge Computing for Quantum Simulation}

\subsubsection{NVIDIA Jetson Platform}

The Jetson Orin Nano represents NVIDIA's edge AI platform featuring:
\begin{itemize}
    \item ARM Cortex-A78AE CPU (6 cores, 1.5 GHz)
    \item NVIDIA Ampere GPU (1024 CUDA cores)
    \item 8GB unified LPDDR5 memory (shared CPU/GPU)
    \item 15W--25W configurable power envelope
\end{itemize}

The unified memory architecture eliminates explicit CPU-GPU data transfers but imposes a strict 8GB limit for all allocations.

\subsubsection{cuQuantum SDK}

NVIDIA's cuQuantum SDK provides GPU-accelerated primitives for quantum circuit simulation:
\begin{itemize}
    \item \textbf{cuStateVec:} State vector operations including gate application and measurement
    \item \textbf{cuTensorNet:} Tensor network contraction for circuit simulation
\end{itemize}

\EdgeQuantum leverages CuPy with cuBLAS for matrix operations, achieving comparable performance to native cuStateVec while maintaining flexibility for custom gate implementations.

\subsection{Memory Scaling in Quantum Simulation}

The state vector for an $n$-qubit system requires $2^n$ complex amplitudes. Using complex64 representation (8 bytes per amplitude):
\begin{equation}
\text{Memory} = 2^n \times 8 \text{ bytes}
\end{equation}

\begin{table}[h]
\centering
\small
\begin{tabular}{cr}
\toprule
\textbf{Qubits} & \textbf{Memory} \\
\midrule
20 & 8 MB \\
24 & 128 MB \\
26 & 512 MB \\
28 & 2 GB \\
30 & 8 GB \\
\bottomrule
\end{tabular}
\caption{State vector memory requirements}
\label{tab:memory_scaling}
\end{table}

For edge devices with 8GB memory, 26--27 qubits represents the practical limit, as intermediate allocations during gate operations require additional memory.
